The limits of self commitment and private paternalism \thanks{}

### 2023-01-18 OA.tex
remove soft arms, edit ss, and main table results

@@

>>>>

\begin{table}[H]
\caption{Balance table conditional on survey \& response rates}
\label{SS_cond_survet}
\begin{center}
\scriptsize{\input{./Tables/SS_cond_survey.tex}}
\end{center}

%\textit{Do file: } \texttt{ss\_att.do}
\end{table}

@@

\subsection{Derivations for Section \ref{sec:randchoice}}

This appendix provides formal proofs of the results described in Section \ref{sec:randchoice}, using the notation and assumptions described in Section \ref{sec:potentialOutcomes}. To simplify the presentation, we omit $i$ subscripts throughout this section.
The following assumption collects our exclusion restriction and the key features of our experimental design.

\begin{assumption}\mbox{}
   \begin{enumerate}[(i)]
   \item $Z$ is independent of $(Y_{0}, Y_{1}, C)$
   \item $D = \mathbbm{1}(Z \neq 2)Z + \mathbbm{1}(Z = 2)C$
   \item $Y = \mathbbm{1}(Z = 0) Y_{0} + \mathbbm{1}(Z = 1) Y_{1} + \mathbbm{1}(Z = 2) [ (1 - C) Y_{0} + C Y_{1}]$
   \end{enumerate}
   \label{assump:randchoice}
\end{assumption}

\begin{lem}\mbox{}
   \begin{enumerate}[(i)]
       \item $\mathbbm{E}(D|Z=2) = \mathbb{P}(C=1)$
       \item $\mathbbm{E}(Y|Z=0) = \mathbbm{E}(Y_0)$
       \item $\mathbbm{E}(Y|Z=1) = \mathbbm{E}(Y_1)$
       \item $\mathbbm{E}(Y|D=0,Z=2) = \mathbbm{E}(Y_0|C=0)$
       \item $\mathbbm{E}(Y|D=1,Z=2) = \mathbbm{E}(Y_1|C=1)$
   \end{enumerate} 
   \label{lem:randchoice}
\end{lem}

\begin{proof}
Part (i) follows because $Z=2$ implies $D=C$ and $Z$ is independent of $C$.  
Parts (ii) and (iii) follow similarly: given $Z=0$ we have $Y = Y_0$, given $Z=1$ we have $Y = Y_1$, and $Z$ is independent of $(Y_0,Y_1)$.
For parts (iv) and (v), first note that Assumption \ref{assump:randchoice} (iii) implies that $Z$ is conditionally independent of $(Y_0,Y_1)$ given $C$.
Now, $Z=2$ implies that $D=0$ if and only if $C=0$. Hence,
\[
\mathbbm{E}(Y|D=0, Z=2) = \mathbbm{E}(Y_0|D=0, Z=2) = \mathbbm{E}(Y_0|C=0, Z=2)=\mathbbm{E}(Y_0|C=0)
\]
establishing part (iv).
Similarly, $Z=2$ implies that $D=1$ if and only if $C=1$ and hence
\[
\mathbbm{E}(Y|D=1, Z=2) = \mathbbm{E}(Y_1|D=1, Z=2) = \mathbbm{E}(Y_1|C=1, Z=2)= \mathbbm{E}(Y_1|C=1)
\]
establishing part (v).
\end{proof}

\begin{prop} \mbox{}
    \begin{enumerate}[(i)]
        \item $\text{ToT} \equiv \mathbbm{E}(Y_1 - Y_0|C=1)  = \displaystyle \frac{\mathbbm{E}(Y|Z=2) - \mathbbm{E}(Y|Z=0)}{\mathbbm{E}(D|Z=2)}$
        \item $\text{TuT} \equiv \mathbbm{E}(Y_1 - Y_0|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y|Z=2)}{1 - \mathbbm{E}(D|Z=2)}$
        \item $\text{ASB} \equiv \mathbbm{E}(Y_0|C=1) - \mathbbm{E}(Y_0|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0)}{\mathbbm{E}(D|Z=2)}$
        \item $\text{ASL} \equiv \mathbbm{E}(Y_1|C=1) - \mathbbm{E}(Y_1|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=2,D=1) - \mathbbm{E}(Y|Z=1)}{1 - \mathbbm{E}(D|Z=2)}$
    \end{enumerate}
\end{prop}

\begin{proof}
For parts (i) and (iii) we require an expression for $\mathbbm{E}(Y_0|C=1)$ in terms of the observables $(Y, D, Z)$.
By Lemma \ref{lem:randchoice}(ii) and iterated expectations
\[
\mathbbm{E}(Y|Z=0) = \mathbbm{E}(Y_0) = \mathbbm{E}(Y_0|C=0) \mathbbm{P}(C=0) + \mathbbm{E}(Y_0|C=1) \mathbbm{P}(C=1).
\]
Re-arranging and substituting Lemma \ref{lem:randchoice}(i) and (iv),
\begin{equation}
\mathbbm{E}(Y_0|C=1)  = \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y_0|C=0) \mathbbm{P}(C=0)}{\mathbbm{P}(C=1)} =  \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0) \mathbbm{E}(1 - D|Z=2)}{\mathbbm{E}(D|Z=2)}.
\label{eq:Y0C1}
\end{equation}
Part (i) follows by combining \eqref{eq:Y0C1} with Lemma \ref{lem:randchoice}(v) and simplifying; part (iii) follows by combining \eqref{eq:Y0C1} with Lemma \ref{lem:randchoice}(iv) and simplifying.
Similarly, for parts (ii) and (iv) we require an expression for $\mathbbm{E}(Y_1|C=0)$ in terms of observables.
By Lemma \ref{lem:randchoice}(iii) and iterated expectations,
\[
\mathbbm{E}(Y|Z=1) = \mathbbm{E}(Y_1) = \mathbbm{E}(Y_1|C=0)\mathbbm{P}(C=0) + \mathbbm{E}(Y_1|C=1) \mathbbm{P}(C=1).
\]
Re-arranging and substituting Lemma \ref{lem:randchoice}(i) and (v),
\begin{equation}
\mathbbm{E}(Y_1|C=0) 
= \frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y_1|C=1)\mathbbm{P}(C=1)}{\mathbb{P}(D=0)} =\frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y|Z=2,D=1)\mathbbm{E}(D|Z=2)}{\mathbb{E}(1-D|Z=2)}.
\label{eq:Y1C0}
\end{equation}
Part (ii) follows by combining \eqref{eq:Y1C0} with Lemma \ref{lem:randchoice}(iv) and simplifying; part (iv) follows by combining \eqref{eq:Y1C0} with Lemma \ref{lem:randchoice}(v) and simplifying.
\end{proof}

%\begin{proof}
%For part (iii), note that 
%\[
%\mathbbm{E}(Y|Z=0) = \mathbbm{E}(Y_0) = \mathbbm{E}(Y_0|C=0) \mathbbm{P}(C=0) + \mathbbm{E}(Y_0|C=1) \mathbbm{P}(C=1)
%\]
%by Lemma \ref{lem:randchoice}(ii) and iterated expectations.
%Re-arranging, 
%\[
%\mathbbm{E}(Y_0|C=1) = \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y_0|C=0) \mathbbm{P}(C=0)}{\mathbbm{P}(C=1)}.
%\]
%Therefore, by Lemma \ref{lem:randchoice} (i) and (iv)
%\begin{align*}
%\mathbbm{E}(Y_0|C=1) - \mathbbm{E}(Y_0|C=0) &= \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0) \mathbbm{E}(1 - D|Z=2)}{\mathbbm{E}(D|Z=2)} - \mathbbm{E}(Y|Z=2, D=0)\\
%&= \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0)}{\mathbbm{E}(D|Z=2)}.
%\end{align*}
%
%Similarly, for part (iv) note that
%\[
%\mathbbm{E}(Y|Z=1) = \mathbbm{E}(Y_1) = \mathbbm{E}(Y_1|C=0)\mathbbm{P}(C=0) + \mathbbm{E}(Y_1|C=1) \mathbbm{P}(C=1)
%\]
%by Lemma \ref{lem:randchoice}(iii) and iterated expectations.
%Rearranging,
%\[
%\mathbbm{E}(Y_1|C=0) = \frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y_1|C=1)\mathbbm{P}(C=1)}{\mathbb{P}(C=0)}.
%\]
%Therefore, by Lemma \ref{lem:randchoice} (i) and (v),
%\begin{align*}
%\mathbbm{E}(Y_1|C=1) - \mathbbm{E}(Y_1|C=0) &= \mathbbm{E}(Y|Z=2, D=1) - \frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y|Z=2, D=1)\mathbbm{E}(D|Z=2)}{\mathbb{P}(C=0)} \\
%&= \frac{\mathbbm{E}(Y|Z=2,D=1) - \mathbbm{E}(Y|Z=1)}{1 - \mathbbm{E}(D|Z=2)}.
%\end{align*}
%\end{proof}

### 2023-01-18 Tables/Attrition.tex
remove soft arms, edit ss, and main table results

% Table generated by Excel2LaTeX from sheet 'Attrition'
\begin{tabular}{lcccccccc}
\toprule
      &       & \multicolumn{3}{c}{Commitment arms} &       & \multicolumn{3}{c}{Soft arms} \\
\cmidrule{3-5}\cmidrule{7-9}      & Control & Forced & Choice & p-value &       & Forced & Choice  & p-value \\
\midrule
\midrule
Number of branch-day pawns & 31    & 33    & 40    & 0.14  &       & 33    & 34    & 0.76 \\
      & (3)   & (2.7) & (3.3) &       &       & (3.2) & (2.2) &  \\
Survey response rate & 0.78  & 0.75  & 0.77  & 0.59  &       & 0.8   & 0.81  & 0.69 \\
      & (0.02) & (0.03) & (0.03) &       &       & (0.03) & (0.02) &  \\
\midrule
Obs   & 1770  & 1954  & 2580  &       &       & 1470  & 1904  &  \\
\bottomrule
\bottomrule
\end{tabular}%

>>>>

% Table generated by Excel2LaTeX from sheet 'Attrition'
\begin{tabular}{lcccc}
\toprule
      &       & \multicolumn{3}{c}{Commitment arms} \\
\cmidrule{3-5}      & Control & Forced & Choice & p-value \\
\midrule
\midrule
Number of branch-day pawns & 34    & 34    & 36    & 0.52 \\
      & (3)   & (2.9) & (1.8) &  \\
\multicolumn{1}{p{12.82em}}{Ended up pawning} & 0.98  & 0.97  & 0.97  & 0.62 \\
      & (0.01) & (0.01) & (0.01) &  \\
Survey response rate & 0.79  & 0.76  & 0.77  & 0.62 \\
      & (0.02) & (0.02) & (0.01) &  \\
\midrule
Obs   & 1770  & 1954  & 2580  &  \\
\bottomrule
\bottomrule
\end{tabular}%
